### 2013-08-17 cws/response.txt

Thank you for your thoughtful feedback and helpful suggestions. We
look forward to revising our paper in light of your comments.
Please allow us to give some detailed answers to Reviewer #2's comments.

> though it's not clear if the improvements over the baselines and previous state-of-the-art systems are significant
Statistical significance tests using the paired bootstrap resampling method with 1000 iterations (Efron and Tibshirani, 1993) shows that our DD algorithm is significantly better than the character-based CRF basedline in F1 score in 4 out of 4 cases on SIGHAN 2005 dataset at 95% confidence level, and is significantly better than the word-based perceptron baseline in 3 out of 4 cases (except for AS) at the same confidence level.
We will report full details in the final writeup upon acceptance.

> I realise space is at a premium but I think the introduction and sections 2.1 and 2.2 could easily be compressed to make room.
Great suggestion! We will make our notations more consistent and provide more details of the DD algorithm.

> They provide no analysis of why Sun 10 outperforms their model on the CU set. It would be interesting to see some discussion regarding this point. 
Sun 2010 did not make their code or system outputs available, therefore it is difficult to obtain a fine-grained comparison of our algorithm with his on the CU set. 
However, there are two high-level differences we observe: 1) Both our chracter-based and word-based baseline systems give numbers that are significantly lower (by more than 1% in F1) on this dataset than Sun 2010; although DD algorithm improves upon both baselines, it is bounded by the quality of the underlying systems. 
2) We did not perform any dataset-specific post-processing in any of our systems since the main focus of the paper is to demonstrate the merits of combining word and character-based systems using the DD algorithm. 
Various reports from the SIGHAN participants have suggested that tricks like number and date normalization post-processing can lead to significant improvements for particular datasets, which could be a factor for the performance difference.

> It converges given one test set but this doesn't constitute a guarantee. It's not a proof.
We apologize for the confusion, but the optimality guarantee that we were referring to is with respect to the constrained-optimization problem of the joint objective (Rush et al. ACL 2010 outlined a proof for the guarantee); we were not stating that the DD algorithm is guaranteed to give the optimal results for the respective task. We will clarify it in the final writeup.

### 2013-08-17 cws/response.txt

Thank you for your thoughtful feedback and helpful suggestions. We
look forward to revising our paper in light of your comments.
Please allow us to give some detailed answers to Reviewer #2's comments.

> though it's not clear if the improvements over the baselines and previous state-of-the-art systems are significant
Statistical significance tests using the paired bootstrap resampling method with 1000 iterations (Efron and Tibshirani, 1993) shows that our DD algorithm is significantly better than the character-based CRF basedline in F1 score in 4 out of 4 cases on SIGHAN 2005 dataset at 95% confidence level, and is significantly better than the word-based perceptron baseline in 3 out of 4 cases (except for AS) at the same confidence level.
We will report full details in the final writeup upon acceptance.

> I realise space is at a premium but I think the introduction and sections 2.1 and 2.2 could easily be compressed to make room.
Great suggestion! We will make our notation more consistent and provide further details on the DD algorithm.

> They provide no analysis of why Sun 10 outperforms their model on the CU set. It would be interesting to see some discussion regarding this point. 
Sun 2010 did not make their code or system outputs available, so it is difficult to obtain a fine-grained comparison of our algorithm with his on the CU set. 
However, there are two high-level differences we observe: 1) Both our chracter-based and word-based baseline systems give numbers that are significantly lower (by more than 1% in F1) on this dataset than Sun 2010; although DD algorithm improves upon both baselines, it is bounded by the quality of the underlying systems. 
2) We did not perform any dataset-specific post-processing in any of our systems since the main focus of the paper is to demonstrate the merits of combining word and character-based systems using the DD algorithm. 
Various reports from the SIGHAN participants have suggested that tricks like number and date normalization post-processing can lead to significant improvements for particular datasets, which could be a factor in the performance difference.

> It converges given one test set but this doesn't constitute a guarantee. It's not a proof.
We apologize for the confusion, but the optimality guarantee that we were referring to is with respect to the constrained-optimization problem of the joint objective (Rush et al. ACL 2010 outlined a proof for the guarantee); we were not stating that the DD algorithm is guaranteed to give optimal results for the given task. We will clarify this in the final writeup.

### 2014-03-12 cws/emnlp_cws/discussion.tex
copyediting updates

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
On the SIGHAN 2005 test set, in over 99.1\% cases the DD algorithm converged within 100 iterations which gives an optimality guarantee. 
In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.

@@

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear use of the word 点心 (``sweets / snack food") and instead attach 点 to the prior word to produce the otherwise common compound 一点点 (``a little bit"); dual decomposition allows the model to generate the correct segmentation.
\begin{footnotesize}
\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{footnotesize}\vspace{-3mm}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.

>>>>

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing \textsc{oov} words than the baseline systems that it combines.
On the SIGHAN 2005 test set, in over 99.1\% of cases the DD algorithm converged within 100 iterations, which gives an optimality guarantee. 
In 77.4\% of the cases, DD converged in the first iteration. The number of iterations to convergence histogram is plotted in Figure~\ref{fig:histo}.

@@

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear use of the word 点心 (``sweets / snack food") and instead attach 点 to the prior word to produce the otherwise common compound 一点点 (``a little bit"); dual decomposition allows the model to generate the correct segmentation.
\begin{footnotesize}
\begin{tabbing}
\ \ \ \ \= \emph{Gloss}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{footnotesize}\vspace{-3mm}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.

### 2014-03-12 cws/emnlp_cws/experiment.tex
copyediting updates

We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}). Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. 
%Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

>>>>

We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.

We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training and sections 400-931 for development in hyper-parameter setting; for all results given in tables, the models are trained and evaluated on the standard train/test split for the given dataset. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; the perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration of 100 ($T$ in Algo.~\ref{algo:DD}) with step size 0.1 ($\alpha_t$ in Algo.~\ref{algo:DD}).

Beyond standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. We also report out-of-vocabulary recall (R$_{\mathrm{oov}}$) as an estimation of the model's generalizability to previously unseen words.

%Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2014-03-12 cws/emnlp_cws/models.tex
copyediting updates

\begin{table*}
\centering
\begin{small}
\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{Academia Sinica} &  \multicolumn{5}{c}{Peking Univ.} \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\ 
Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
Word-based Perceptron &  95.8 & \textbf{95.0} & \textbf{95.4}  & \textbf{69.5} & 0.060  &  94.1             & 95.5  & 94.8  &  76.7 & 0.099     \\ 
Dual-decomp      & \textbf{95.9} & 94.9   & \textbf{95.4}  & {67.7} & \textbf{0.055}            & \textbf{94.8} & \textbf{95.7} & \textbf{95.3}  &  \textbf{78.7} & \textbf{0.086}   \\
%\cline{2-9}
\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{City Univ. of Hong Kong} &  \multicolumn{5}{c}{Microsoft Research}  \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{Consist}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{Consist} \\ 
Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7                                         & 0.073              &  97.0 &              97.2                & 97.1  & 74.6 & 0.063  \\
Dual-decomp                   & \textbf{95.0} & \textbf{94.4}  & \textbf{94.7}  & {75.3} & \textbf{0.062} & \textbf{97.3} &  \textbf{97.4} &  \textbf{97.4}  & \textbf{76.0} & \textbf{0.055}  \\
\end{tabular} 
\caption{Results on SIGHAN 2005 datasets. \textit{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and \textit{Consist} denotes segmentation consistency. Best number in each column is highlighted in bold.
%$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. 
}\label{tbl:results}
\end{small}
\end{table*}

@@

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitations, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

>>>>

\begin{table*}
\centering
\begin{small}
\begin{tabular}{ r | c | c | c | c | c | c | c | c | c | c  }
%\multicolumn{13}{c}{\large{SIGHAN 2005}} \\
\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{Academia Sinica} &  \multicolumn{5}{c}{Peking Univ.} \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\ 
Char-based CRF    &  95.2 &   93.6  & 94.4  &  58.9 & 0.064                                               &  94.6             &    95.3 & 94.9  &   77.8   & 0.089    \\
Word-based Perceptron &  95.8 & \textbf{95.0} & \textbf{95.4}  & \textbf{69.5} & 0.060  &  94.1             & 95.5  & 94.8  &  76.7 & 0.099     \\ 
Dual-decomp      & \textbf{95.9} & 94.9   & \textbf{95.4}  & {67.7} & \textbf{0.055}            & \textbf{94.8} & \textbf{95.7} & \textbf{95.3}  &  \textbf{78.7} & \textbf{0.086}   \\
%\cline{2-9}
\multicolumn{1}{c|}{} &  \multicolumn{5}{c|}{City Univ. of Hong Kong} &  \multicolumn{5}{c}{Microsoft Research}  \\
\hline
\multicolumn{1}{c}{}   & \multicolumn{1}{|c}{R} &  \multicolumn{1}{c}{P}     &  \multicolumn{1}{c}{F$_1$}   &    \multicolumn{1}{c}{R$_{\mathrm{oov}}$}   &   \multicolumn{1}{c}{C}  & \multicolumn{1}{|c}{R}  &  \multicolumn{1}{c}{P}   &  \multicolumn{1}{c}{F$_1$}   &   \multicolumn{1}{c}{R$_{\mathrm{oov}}$}  &   \multicolumn{1}{c}{C} \\ 
Char-based CRF                 & 94.7 & 94.0 & 94.3  & \textbf{76.1}                            & 0.065             & 96.4 &              96.6 &             96.5  & 71.3 & 0.074 \\
Word-based Perceptron    & 94.3 & 94.0 & 94.2  & 71.7                                         & 0.073              &  97.0 &              97.2                & 97.1  & 74.6 & 0.063  \\
Dual-decomp                   & \textbf{95.0} & \textbf{94.4}  & \textbf{94.7}  & {75.3} & \textbf{0.062} & \textbf{97.3} &  \textbf{97.4} &  \textbf{97.4}  & \textbf{76.0} & \textbf{0.055}  \\
\end{tabular} 
\caption{Results on SIGHAN 2005 datasets. \textit{R$_{\mathrm{oov}}$}  denotes \textsc{oov} recall, and \textit{C} denotes segmentation consistency. Best number in each column is highlighted in bold.
%$\dagger$ and $\ddagger$ denote statistical significance ($p<0.01$) against CRF and perceptron baselines, respectively. 
}\label{tbl:results}
\end{small}
\end{table*}

@@

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for the DD algorithm in Algo.~\ref{algo:DD}.\footnote{See \newcite{Rush:2012:JAIR} for a full introduction to DD.}
